Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-10-23 exp1/present2013.tex
Comment out things to shorten
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@690 43ef1190-90fd-4dd7-a769-d0121f02b80e

%\documentclass[english,aspectratio=196]]{ifislide}
%\documentclass[english,print,aspectratio=169]{ifislide}
%\documentclass[english,handout,aspectratio=169]{ifislide}
\documentclass[english,usenames,dvipsnames,aspectratio=169,handout]{beamer}
\usepackage{verbatim}
\usepackage{config}
\usepackage{pgf}
\usepackage{pgfpages}

%
%  Load other packages you may need here
% 
% \pgfpagesuselayout{4 on 1}[a4paper,landscape,border shrink=5mm
\pgfpagesuselayout{2 on 1}[a4paper,border shrink=5mm]

@@

\setbeameroption{show notes}
\usepackage[utf8]{inputenc}

@@

\note{
  \begin{itemize}
  \item Those that are deemed significant are labelled.
  \item Don't worry about the axes
  \item Yes, the Implementation is better, we knew that, 
  \item Interactions with Implement with joins are
    naturally strong
  \item ``Union'', ``Optional'' and ``Lang'' demanding things
  \item ``BGPComp:Lang'' and ``Lang:Union'' interactions might be due
    to that many more triples need to be searched for a language tag
    in one of the levels of the interacting factors.
  \item But what about ``Implement::TripleC''? Leave that hanging for
    a bit.
  \item We want to do a hypothesis test
  \item Two factors do not contribute significantly to the variation
    ``Range'' and ``Machine'', in the paper we describe how this
    enables us to average over certain factors and look upon the rest
    as a replicated experiment.
  \end{itemize}
}

@@

\end{frame}
\note{
  \begin{itemize}
  \item ``Machine'' is a broad factor, good idea to group to manage
    complexity, can be broken down later
  \item ``TripleC:Machine'' and ``TripleC'' highly significant,
    implies the factors were wrongly set.
  \item This invalidates the preceeding experiments. We got
    strong indications early on. This is one of the strategies for
    falsification we outline.
  \item This experiment is also invalidated by the absence of certain
    features, such as language modifiers.
\end{itemize}
}

>>>>

%\documentclass[english,aspectratio=196]]{ifislide}
%\documentclass[english,print,aspectratio=169]{ifislide}
%\documentclass[english,handout,aspectratio=169]{ifislide}
%\documentclass[english,usenames,dvipsnames,aspectratio=169,handout]{beamer}
\documentclass[english,usenames,dvipsnames,aspectratio=169]{beamer}
\usepackage{verbatim}
\usepackage{config}
\usepackage{pgf}
\usepackage{pgfpages}

%
%  Load other packages you may need here
% 
% \pgfpagesuselayout{4 on 1}[a4paper,landscape,border shrink=5mm
%\pgfpagesuselayout{2 on 1}[a4paper,border shrink=5mm]

@@

%\setbeameroption{show notes}
\usepackage[utf8]{inputenc}

@@

\note{
  \begin{itemize}
  \item Those that are deemed significant are labelled.
  \item Don't worry about the axes
  \item Yes, the Implementation is better, we knew that, 
  \item Interactions with Implement with joins are
    naturally strong
  \item ``Union'', ``Optional'' and ``Lang'' demanding things
%  \item ``BGPComp:Lang'' and ``Lang:Union'' interactions might be due
%    to that many more triples need to be searched for a language tag
%    in one of the levels of the interacting factors.
  \item But what about ``Implement::TripleC''? Leave that hanging for
    a bit.
  \item We want to do a hypothesis test
  \item Two factors do not contribute significantly to the variation
    ``Range'' and ``Machine'', in the paper we describe how this
    enables us to average over certain factors and look upon the rest
    as a replicated experiment.
  \end{itemize}
}

@@

\end{frame}
\note{
  \begin{itemize}
  \item ``Machine'' is a broad factor, good idea to group to manage
    complexity, can be broken down later
  \item ``Implement:TripleC'' and ``TripleC'' highly significant,
    implies the factors were wrongly set.
  \item This invalidates the preceeding experiments. We got
    strong indications early on. This is one of the strategies for
    falsification we outline.
  \item This experiment is also invalidated by the absence of certain
    features, such as language modifiers.
\end{itemize}
}
